\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm,enumerate}
\usepackage[]{graphicx}
\usepackage{color,subfigure}
\usepackage{multicol}
\usepackage{float}
\usepackage[all]{xypic}
\usepackage[colorlinks=true,citecolor=cyan,linkcolor=magenta]{hyperref}
\usepackage{colonequals}

\usepackage{fancyhdr, lastpage}
\pagestyle{fancy}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}


\DeclareMathOperator{\Spec}{Spec}

\title{}
\date{\vspace{-0.5in}}

\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

\theoremstyle{definition}
\newtheorem{problem}{Problem}


\title{Homework 1}

\begin{document}

\thispagestyle{fancy}
\pagestyle{fancy}
\rhead{UNL $\mid$ Elo\'isa Grifo}
\lhead{Commutative Algebra I Fall 2022}

\vspace{3em}

\begin{center}
	{\LARGE Problem Set 3}
\end{center}

\

\noindent
{\bf Instructions:}
For full credit, turn in 4 problems in a pdf file. 
You are welcome to work together with your classmates on all the problems, and I will be happy to give you hints or discuss the problems with you, but you should write up your solutions by yourself.
You cannot use any resources besides me, your classmates, our course notes, and the Macaulay2 documentation.


\vspace{0.6em}
%
%\begin{problem}
%	In Macaulay2, set up a polynomial ring $R$ over a field $k$, a nontrivial ideal $I$ in $R$, the $R$-module $M = R/I$ and the ring $S = R/I$. Your work must be turned in as (part of) a .m2 file.
%\end{problem}



\begin{problem}
	Let $k$ be a field, $x$ an indeterminate, and $R \colonequals k[x^2, x^3] \subseteq S \colonequals k[x]$. Find an ideal $I$ in $R$ such that $IS \cap R \supsetneq I$.
\end{problem}

\begin{problem}
Let $k$ be an infinite field, $m \geqslant 1$, and let $R = k[x_1,\dots, x_n]$ be a polynomial ring. Let $G= (k^\times)^m$ act on $R$ as follows: 
\[ \begin{aligned} (\lambda_1,\dots,\lambda_m) \cdot c &= c \qquad & \textrm{for }c \in k,\\
 (\lambda_1,\dots,\lambda_m) \cdot x_i &= \lambda_1^{a_{1i}} \cdots  \lambda_m^{a_{mi}} x_i \qquad & {i=1,\dots,n}
 \end{aligned}\]
 for some $m \times n$ matrix of integers $A=[a_{ij}]$.
\begin{enumerate}[a)]
\item Show that $R^G$ has a $k$-vector space basis given by the set of monomials $x_1^{b_1} \cdots x_n^{b_n}$ such that, for $b=(b_1,\dots,b_n)$, $Ab=0$.
\item Consider the polynomial ring $R$ with a (nonstandard) $\mathbb{Z}^m$-grading given by setting 
$$\textrm{deg}(x_i) = (a_{1i},\dots,a_{mi})$$ 
for each $i$. Show that $R^G$ is the degree zero piece of $R$ under this grading.
\item Show that $R^G$ is a direct summand of $R$, and conclude that $R^G$ is a finitely generated $k$-algebra.
\item Let $R = k[x,y,z,w]$ and consider the $k$-linear action of $G = k^\times$ on $R$ given by
$$\lambda \cdot x = \lambda x \qquad \lambda \cdot y = \lambda y \qquad \lambda \cdot z = \lambda^{-1} z \qquad \lambda \cdot w = \lambda^{-1} w.$$
Find a finite set of generators for $R^G$ as a $k$-algebra.
\end{enumerate}
\end{problem}

%\begin{problem}
%Given two ideals $I$ and $J$, the \emph{product} of $I$ and $J$ is the ideal
%$$IJ \colonequals \left( fg \mid f \in I \textrm{ and } g \in J \right) .$$
%\begin{enumerate}[a)]
%	\item Show that $IJ \subseteq I \cap J$.
%	\item If $I$ and $J$ satisfy $I+J = R$, then $IJ = I \cap J$.
%	\item In general, $IJ \neq I \cap J$. Find an example of a ring $R$ and ideals $I$ and $J$ with $IJ \neq I \cap J$.
%\end{enumerate}
%\end{problem}
%
%
%
%
%\begin{problem}	
%Let $I$ and $J$ be ideals in a ring $R$.
%\begin{enumerate}[a)]
%\item Show that $\sqrt{\sqrt{I}} = \sqrt{I}$.
%\item Show that if $I \subseteq J$, then $\sqrt{I} \subseteq \sqrt{J}$.
%\item Show that $\sqrt{I \cap J} = \sqrt{I} \cap \sqrt{J}$.
%\item Show that $\sqrt{I^n} = \sqrt{I}$ for all $n \geqslant 1$.
%\item Show that if $P$ is a prime ideal, then $\sqrt{P^n} = P$ for all $n \geqslant 1$.
%\end{enumerate}
%\end{problem}





\begin{problem}
	Consider the inclusion map $k[xy,xz,yz] \subseteq k[x,y,z]$, where $k$ is a field. Is the induced map on Spec surjective? If not, give an explicit prime not in the image.
\end{problem}


\


\noindent
\fbox{\begin{minipage}{\textwidth}
Let $R$ be a ring of prime characteristic $p$, meaning that the smallest $n>0$ such that
$$\underset{n \textrm{ times}}{\underbrace{1 + \cdots + 1}} = 0$$
is $n = p$. Then the map $F\!: R \to R$ given by $F(r) = r^p$ is a ring homomorphism, called the {\bf Frobenius map}.
\end{minipage}} 

\begin{problem}
	Let $R$ be a ring of prime characteristic $p$. 
	\begin{enumerate}[a)]
	\item Show that the Frobenius map is injective if and only if $\sqrt{(0)} = (0)$.
	\item Show that the $F(R) \subseteq R$ is module-finite if and only if it is algebra-finite.
	\item Show that the map on spectra induced by the Frobenius map is the identity map.
	\end{enumerate}
\end{problem}


\newpage

\noindent
\fbox{\begin{minipage}{\textwidth}
A topological space is \emph{irreducible}\index{irreducible space} if it cannot be written as a union of two proper closed subsets.
\end{minipage}} 
\begin{problem}
	Let $R$ be a ring and be an ideal in $I$. Show that $V(I)$ is irreducible if and only if $\sqrt{I}$ is prime.
\end{problem}

\end{document}