\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm,mathrsfs}
\usepackage[]{graphicx}
\usepackage{color,subfigure}
\usepackage{multicol}
\usepackage{enumerate}
\usepackage{colonequals}
\usepackage{float}
\usepackage[all]{xypic}
\usepackage[colorlinks=true,citecolor=cyan,linkcolor=magenta]{hyperref}
\usepackage{stmaryrd}
\usepackage[bottom]{footmisc}



\usepackage{fancyhdr, lastpage}
\pagestyle{fancy}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}


\DeclareMathOperator{\Ch}{Ch}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\im}{im}
\newcommand{\m}{\mathfrak{m}}
\DeclareMathOperator{\ann}{ann}


\title{}
\date{\vspace{-0.5in}}

\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

\theoremstyle{definition}
\newtheorem{problem}{Problem}


\title{Problem Set 4}

\begin{document}

\thispagestyle{fancy}
\pagestyle{fancy}
\rhead{UCR $\mid$ Elo\'isa Grifo}
\lhead{Homological Algebra Spring 2021}


\begin{center}
	{\LARGE Problem Set 4}
\end{center}



\begin{problem}
	Let $R=k[x,y]$, where $k$ is a field, let $Q = \textrm{frac}(R)$ be the fraction field of $R$. We are going to show that the $R$-module $M = Q/R$ is divisible but not injective.
	\begin{enumerate}[a)]
		\item Show that if $ax + by = 0$ for some $a, b \in R$, we must have $b \in (x)$.
		\item Show that $x \mapsto \frac{1}{y}$ and $y \mapsto 0$ induces a well-defined $R$-module homomorphism $(x,y) \xrightarrow{\, f \,} Q/R$.
		\item Show that $M$ is a divisible $R$-module, but not injective.
	\end{enumerate}
\end{problem}



\vfill

\begin{problem}
	Let $R$ be a domain. Show that if $R$ has a nonzero module $M$ that is both injective and projective, then $R$ must be a field.\footnote{Hint: show that any nonzero $R$-module homomorphism $M \longrightarrow R$ must be surjective, and then show that such a homomorphism must exist.}
\end{problem}



\vfill


\begin{problem}
	Let $R$ be a Noetherian ring, $M$ a finitely generated $R$-module, $N$ an $R$-module, and $W$ a multiplicatively closed subset of $R$. Show that there is an isomorphism
	$$W^{-1} \Hom_R(M,N) \cong \Hom_{W^{-1} R}(W^{-1}M,W^{-1}N).$$
	Clearly indicate where you are using the hypotheses that $R$ is Noetherian and $M$ is finitely generated, as they are necessary.\footnote{Hint: start by noting that the obvious map $W^{-1} \Hom_R(M,N) \longrightarrow \Hom_{W^{-1} R}(W^{-1}M,W^{-1}N)$ is natural on $M$ and an isomorphism when $M = R^n$. Then apply appropriate functors to a presentation $R^m \longrightarrow R^n \longrightarrow M$ for $M$.}
\end{problem}



\vfill

\begin{problem} Let $\mathcal{A}$ be an abelian category.
	\begin{enumerate}[a)]
		\item Show that $\ker(x \xrightarrow{0} y) = 1_x$,  $\coker(x \xrightarrow{0} y) = 1_y$, and $\im(x \xrightarrow{0} y) = 0 \longrightarrow y$.
		\item Show that $f$ is a mono if and only if $fg = 0$ implies $g = 0$, and $g$ is an epi if and only if $fg = 0$ implies $f = 0$.
		\item Show that $f$ is a mono if and only if $\ker f = 0$, and $g$ is an epi if and only if $\coker g = 0$.
		\item Show that $0 \longrightarrow A \xrightarrow{\, f \,} B$ is exact if and only if $f$ is a mono.
		\item Show that $B \xrightarrow{\, g \,} C \longrightarrow 0$ is exact if and only if $g$ is an epi.
	\end{enumerate}
\end{problem}



\vfill

\begin{problem}
Consider an abelian category. If $g$ is an epi and $f$ is a mono, then $\ker (fg) = \ker g$, $\coker(fg) = \coker f$, and $\im (fg) = \im f = f$.
\end{problem}


\newpage


\noindent
\fbox{\begin{minipage}{\textwidth}
An $R$-module $F$ is \emph{faithfully flat} if $F$ is flat and $F \otimes_R M \neq 0$ for every nonzero $R$-module $M$.
\end{minipage}} 

\vspace{1em}

\begin{problem} Give an example of a module that is flat but not faithfully flat. Show\footnote{Hints: \begin{itemize}
	\item For $c) \implies a)$, for each $R$-module $M \neq 0$ consider some nonzero $m \in M$ and $I = \ann m$. 
	\item For $a) \implies d)$, show that $\im(1_F \otimes f) = F \otimes_R \im f$ and $\ker(1_F \otimes f) = F \otimes_R \ker g$, and then consider the short exact sequence $0 \longrightarrow \im f \longrightarrow \ker g \longrightarrow \ker g/\im f \longrightarrow 0$. 
	\item For $d) \implies a)$, show that for any $R$-module $M \neq 0$, the identity map on $M$ induces a nonzero map $F \otimes_R M \longrightarrow R \otimes_R M$.
\end{itemize}}
 that the following are equivalent:	
\begin{enumerate}[a)]
		\item $F$ is faithfully flat.
		\item $F$ is flat and for every proper ideal $I$, $IF \neq F$.
		\item $F$ is flat and for every maximal ideal $\m$, $\m F \neq F$.
		\item For every sequence of $R$-modules $\xymatrix{A \ar[r]^-f & B \ar[r]^-g & C}$, $\xymatrix{A \ar[r]^-f & B \ar[r]^-g & C}$ is exact if and only if $\xymatrix{F \otimes_R A \ar[r]^-{1 \otimes f} & F \otimes_R B \ar[r]^-{1 \otimes g} & F \otimes_R C}$ is exact.
	\end{enumerate}
\end{problem}

\vspace{2em}

\begin{problem}
	Consider the ring $R = \mathbb{Q}[x,y,z,a,b,c]/(xb-ac,yc-bz,xc-az)$, the ideal $I = (x,a)$ in $R$, $I = (x,a)$, and the $2$-generated $R$-module $M = Rf + Rg$, where the generators $f, g$ satisfy the relations 
		$$yf-xg = 0 \quad bf - cg = 0 \quad cf - zg = 0.$$
		Let $S = \mathbb{Q}[x,y,z]$ and $P$ be the ideal in $R$ defining the curve $\lbrace (t^{13},t^{42},t^{73}) \mid t \in \mathbb{Q} \rbrace$.
		\begin{enumerate}[a)]
			\item Find the first $6$ steps in the minimal free resolutions for $R/I$ and $N$ over $R$.
			\item Apply $\Hom_R(-,M)$ to the portion of a minimal free resolution you found for $R/I$. Is this an exact complex? If not, in what homological degrees do we have non-trivial homology? 
			\item Find a minimal free resolution for $P$ over $S$. Make sure your resolution *is* minimal!
		\end{enumerate}
\end{problem}

\end{document}