\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm,enumerate}
\usepackage[]{graphicx}
\usepackage{color,subfigure}
\usepackage{multicol}
\usepackage{float}
\usepackage[all]{xypic}
\usepackage{colonequals}
\usepackage{hyperref}
\usepackage{stmaryrd}

\usepackage{fancyhdr, lastpage}
\pagestyle{fancy}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}

\DeclareMathOperator{\Ass}{Ass}
\DeclareMathOperator{\Min}{Min}
\DeclareMathOperator{\depth}{depth}
\DeclareMathOperator{\pdim}{pdim}

\title{}
\date{\vspace{-0.5in}}

\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

\theoremstyle{definition}
\newtheorem{problem}{Problem}


\title{Problem Set 0 \\ Introductory Macaulay2 problems}


\begin{document}

\thispagestyle{fancy}
\pagestyle{fancy}
\rhead{UNL $\mid$ Elo\'isa Grifo}
\lhead{Math 918 $\mid$ Spring 2022}


\begin{center}
	{\LARGE Problem Set 3\\
	
%	\vspace{0.5em}
	
%	Symbolic powers
}
\end{center}

\

To solve these problems, you are not allowed to use any additional Macaulay2 packages besides the \texttt{Complexes} package and the ones that are automatically loaded with Macaulay2.

\begin{problem}
	Show that if $R$ is a regular local ring then $R_P$ is regular for every prime $P$.
\end{problem}



\begin{problem}[2]
	Of the following rings, which ones are regular? Which ones are Cohen-Macaulay?
	\begin{itemize}
		\item $R = \mathbb{F}_{101}[ X ]/I_2(X)$, where $X$ is a generic $2 \times 3$ matrix.
		\item $S = \mathbb{Q}[x^2,xy,y^2]$.
		\item $T = k \llbracket x,y,z,w \rrbracket/(x^2,xy,yz,zw,w^2)$, where $k$ is any field.
		\item $U = k \llbracket x,y,z \rrbracket /(x+y+z)$, where $k$ is any field.
		\item $V = \mathbb{Q} \begin{bmatrix} ux & uy & uz \\ vx & vy & vz \end{bmatrix} \subseteq \frac{\mathbb{Q}[u,v,x,y,z]}{(x^3+y^3+z^3)}$.
	\end{itemize}
\end{problem}



\begin{problem}
	Consider the ring $R = \mathbb{Q}[x,y,z,a,b,c]/(xb-ac,yc-bz,xc-az)$ and the $2$-generated $R$-module $M = Rf + Rg$, where the generators $f, g$ satisfy the relations 
		$$yf-xg = 0 \quad bf - cg = 0 \quad cf - zg = 0.$$
		Let $P$ be the ideal in $S = \mathbb{Q}[x,y,z]$ defining the curve parametrized by $(t^{13},t^{42},t^{73})$.

\begin{enumerate}[a)]
	\item Find $\pdim(S/P)$ and $\depth(S/P)$.
	\item Is there a regular sequence that generates $P$?
	\item Find $\pdim_R(M)$ and $\depth(M)$.
	\item Is $R$ a regular ring? Is it Cohen-Macaulay?
\end{enumerate}
\end{problem}


\begin{problem}
	Let $k$ be any field and consider the prime ideal in $k[x,y,z]$
	$$P = (x^3-yz,y^2-xz,z^3-x^2y)$$
	defining the curve parametrized by $(t^3, t^4, t^5)$. Give (with proof!) two different ideals $J$ such that $P^{(n)} = (P^n : J^\infty)$ for all $n \geqslant 1$, and test your proposed ideals $J$ in Macaulay2 with your own choice of $k$, $c$, and $n$.
\end{problem}


\end{document}