\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm,enumerate}
\usepackage[]{graphicx}
\usepackage{color,subfigure}
\usepackage{multicol}
\usepackage{float}
\usepackage[all]{xypic}
\usepackage[colorlinks=true,citecolor=cyan,linkcolor=magenta]{hyperref}

\usepackage{fancyhdr, lastpage}
\pagestyle{fancy}
\fancyfoot[C]{{\thepage} of \pageref{LastPage}}


\title{}
\date{\vspace{-0.5in}}

\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

\theoremstyle{definition}
\newtheorem{problem}{Problem}


\title{Homework 1}

\begin{document}

\thispagestyle{fancy}
\pagestyle{fancy}
\rhead{UCR $\mid$ Elo\'isa Grifo}
\lhead{Commutative Algebra Winter 2021}


\begin{center}
	{\LARGE Problem Set 4}
\end{center}


\begin{problem}
	Let $M$ a Noetherian $R$-module. 
	
	\begin{enumerate}[a)]
	\item Show that every surjective $R$-module homomorphism $M \longrightarrow M$ is an isomorphism.
	\item Must an injective $R$-module homomorphism $M \longrightarrow M$ be an isomorphism?
	\end{enumerate}
\end{problem}

\begin{problem}
	Show that $M$ is a Noetherian $R$-module if and only if $M$ is finitely generated and $R/\textrm{ann } M$ is a Noetherian ring.
\end{problem}

\begin{problem}$\,$
\begin{enumerate}[a)]
	\item Let $(R, \mathfrak{m})$ be a local domain that is not a field. Show that the fraction field of $R$ is not a finitely generated $R$-module.
	\item Let $I$ be a proper ideal in a local ring $(R, \mathfrak{m})$, and $M$ a finitely generated $R$-module. Show that if $IM = M$, then $M = 0$.
\end{enumerate}
	\end{problem}


\begin{problem}
	Is there an upper bound for the minimal number of generators of an ideal in $k[x,y]$? Here $k$ is a field. Either prove there is an upper bound or find ideals $I$ with arbitrarily large $\mu(I)$.
\end{problem}



\begin{problem}
	Show that the containment of ideals is a local property: given any ideals $I$ and $J$ in a ring $R$,
	$$I \subseteq J \Longleftrightarrow I_P \subseteq J_P \textrm{ for all } P \in \textrm{Spec}(R).$$	
\end{problem}



\begin{problem}$\,$
	\begin{enumerate}[a)]
		\item Describe $\textrm{supp}(I/I^2)$, where $I = (xz)$ in $R = \mathbb{C}[x,y,z]/(xy,yz)$.		\item Find all the minimal primes of $J = (ab,bc,cd,ad)$ in $k[a,b,c,d]$ over any field $k$.
		\item Find the minimal primes of the ring $S$, where
		$$S = \mathbb{Q} \begin{bmatrix} ux & uy & uz \\ vx & vy & vz \end{bmatrix} \subseteq \frac{\mathbb{Q}[u,v,x,y,z]}{(x^3+y^3+z^3)}.$$
		\item Let $I$ be the defining ideal of the curve parametrized by $(t^{13},t^{42},t^{73})$ over $\mathbb{Q}$. Find $\mu(I)$ and a minimal generating set for $I$.
	\end{enumerate}
\end{problem}


\begin{problem}
Let $R=\mathbb{Q}[x,y,z]$, and $I=(x^3, x^2y, x^2z, xyz)$. Find a prime filtration of $R/I$ and a primary decomposition of $I$.	
\end{problem}



\begin{problem}
	Let $R$ be a Noetherian ring, $x \in R$, and $I$ be an ideal. Show that if $x$ is not in any of the associated primes of $R/I$, then $(x)I = (x) \cap I$.
\end{problem}


\end{document}